\graphicspath{{members/nh/figures/}}

\subsection{Simulation Part Niusha}
\input{members/nh/authors}

A texture appears on the surface of the meshes and representing the look and material of an object. Ameshis a collection of vertices, edges, and faces that describe the shape of a 3D object.Here we used a texture of a soil which is downloaded from www.texture.com. The advantage of using texture vs. image is that it is not necessary to place the image on each coordination to make it look 3D. Scripting is usedto automate the process of creating and placing nets under each plant. plane = bpy.context.selected_objects[0] print('\nPlane coordinates: X: ' + str(plane.location.x) + ' Y:'+ str(plane.location.y) + '\n') mat=bpy.data.materials.new('materialA') bpy.context.object.data.materials.append(mat) mat.use_nodes = TrueLinked nodes using BSDF principal are defined, which is used for shading textures. bsdf = mat.node_tree.nodes["Principled BSDF"]The downloaded Texture is going to import on each material. texImage = mat.node_tree.nodes.new('ShaderNodeTexImage') texImage.image = bpy.data.images.load("C:/My Documents/Blender/Textur.jpg") mat.node_tree.links.new(bsdf.inputs['Base Color'], texImage.outputs['Color'])ImageImageImageLichtThere is a light source above each plant. Light in Blender 2.8 changed from the name lamp to light.There are ... types of light :Point light is a directional point of light. The light power and size can be easily changed. The power is in Watt and the point light with a larger size has softer shadows and specular highlights.# create light datablock, set attributes light_data = bpy.data.lights.new(name="light_2.80", type='SPOT') light_data.energy = 50 # create new object with our light datablock
 light_object = bpy.data.objects.new(name="light_2.80", object_data=light_data # link light object bpy.context.collection.objects.link(light_object) # make it active  bpy.context.view_layer.objects.active = light_objectImageSpot light is a cone shape beam of light. Just like point light the power of the light is in Watt and the larger size has softer shadows and specular highlights.Area light simulates light originating from a surface. This kind of light is like TV screen or window. Beside the power it also has properties shape and size. The shape of Area light can be rectangle, square, disk, ellipse and the size is defined the dimensions for the square and rectangle.
Sun light provides light of constant intensity emitted in a single direction from infinity far away. It is represented by a encircled black dot with dots emitting from it.
